Camellia

### 2012-03-03 docs/presentations/nate/Rodeo2012/talk.tex
Final version of FE Rodeo talk.
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@353 36274a68-8941-4c93-80ef-affaed5139da

Bases are objects.  So are the discrete spaces and element types.  To minimize memory footprint (among
other considerations), we need a mechanism to guarantee that we only create one copy of each basis, discrete
space, and element type.  This is known as a \emph{Factory} in the design pattern literature.

@@

The mathematician's norm for my Stokes formulation is:
\begin{align*}
\NVRnorm{(\NVRvect{q}_{1},\NVRvect{q}_{2},v_{1},v_{2},v_{3})}_{V}^{2}  \NVReqdef \NVRsumm{i=1}{2} ||\NVRvect{q}_{i}||_{\NVRHdiv}^{2} + \NVRsumm{i=1}{3} ||v||_{\NVRHgrad}^{2} \label{NVR:eq:genericNorm}\\
\end{align*}

Compare the quasi-optimal test norm:
\begin{align*}
& \NVRnorm{\frac{q_{11}}{2\mu}+\NVRpd{}{x}v_{1}}_{L^2}^{2} + \NVRnorm{\frac{q_{11}}{2\mu}+\frac{q_{22}}{2\mu}}_{L^2}^{2} + \NVRnorm{\frac{q_{12}}{2\mu}+\frac{q_{21}}{2\mu}+\NVRpd{}{y}v_{1}+\NVRpd{}{x}v_{2}}_{L^2}^{2}\\
&\left. + \NVRnorm{\frac{q_{22}}{2\mu}+\NVRpd{}{y}v_{2}}_{L^2}^{2} + \NVRnorm{q_{12}-q_{21}}_{L^2}^{2} + \NVRnorm{\NVRdiv \NVRvect{q}_{1}-\NVRpd{}{x}v_{3}}_{L^2}^{2} \right.\\
&+\NVRsumm{i=1}{2} ||\NVRvect{q}_{i}||_{L^{2}}^{2} + \NVRsumm{i=1}{3} ||v||_{L^{2}}^{2}\\
\end{align*}

@@

%===============================================================================
% CURRENT AND FUTURE WORK
%===============================================================================
\begin{frame}
\frametitle{Current and Future Work}
\begin{block}{}
\begin{itemize}
\item Nonlinear PDE support
\item MPI---have: distributed stiffness computation and solve (MUMPS); want: distributed storage/mesh
\item Application to Navier-Stokes
\end{itemize}
\end{block}

>>>>

Each element has a type; each type has a pair of discrete spaces; each discrete space is made up of several bases.  How do we keep this design from taking a prohibitive amount of memory?\\
\vspace{3 mm}
For this, among other considerations: want a way to guarantee that we only create one copy of each basis, discrete
space, and element type.  This is known as a \emph{Factory} in the design pattern literature.

@@

The mathematician's norm for my Stokes formulation is:
\begin{align*}
\NVRnorm{(\NVRvect{q}_{1},\NVRvect{q}_{2},v_{1},v_{2},v_{3})}_{V}^{2}  \NVReqdef \NVRsumm{i=1}{2} ||\NVRvect{q}_{i}||_{\NVRHdiv}^{2} + \NVRsumm{i=1}{3} ||v_{i}||_{\NVRHgrad}^{2} \label{NVR:eq:genericNorm}\\
\end{align*}

Compare the quasi-optimal test norm:
\begin{align*}
& \NVRnorm{\frac{q_{11}}{2\mu}+\NVRpd{}{x}v_{1}}_{L^2}^{2} + \NVRnorm{\frac{q_{11}}{2\mu}+\frac{q_{22}}{2\mu}}_{L^2}^{2} + \NVRnorm{\frac{q_{12}}{2\mu}+\frac{q_{21}}{2\mu}+\NVRpd{}{y}v_{1}+\NVRpd{}{x}v_{2}}_{L^2}^{2}\\
&\left. + \NVRnorm{\frac{q_{22}}{2\mu}+\NVRpd{}{y}v_{2}}_{L^2}^{2} + \NVRnorm{q_{12}-q_{21}}_{L^2}^{2} + \NVRnorm{\NVRdiv \NVRvect{q}_{1}-\NVRpd{}{x}v_{3}}_{L^2}^{2} \right.\\
&+\NVRsumm{i=1}{2} ||\NVRvect{q}_{i}||_{L^{2}}^{2} + \NVRsumm{i=1}{3} ||v_{i}||_{L^{2}}^{2}\\
\end{align*}

@@

%===============================================================================
% CURRENT AND FUTURE WORK
%===============================================================================
\begin{frame}
\frametitle{Current and Future Work}
\begin{block}{}
\begin{itemize}
\item Nonlinear PDE support
\item Better scalability (distributed mesh)
\item Application to Navier-Stokes
\end{itemize}
\end{block}
